Cross-Loop Optimization of Arithmetic Intensity for Finite Element Local Assembly

### 2014-10-29 TACO-paper-v2/coffee.tex
minor edits

We address, in particular, the well-known problem of optimizing the local assembly
phase of the finite element method \cite{Francis,quadrature1,petsc-integration-gpu,Kirby-FEM-opt},
which can be responsible for a significant fraction of the overall computation
run-time, often in the range 30-60$\%$. With respect to these studies,
we propose a novel set of composable code transformations targeting, for
the first time, cross-loop arithmetic intensity, with emphasis on instruction-level
parallelism, redundant computation, and register locality. How such transformations
generalize to domains other than finite element local assembly will also be discussed.

>>>>

In particular, we address the well-known problem of optimizing the
local assembly phase of the finite element method
\cite{Francis,quadrature1,petsc-integration-gpu,Kirby-FEM-opt}, which
can be responsible for a significant fraction of the overall
computation run-time, often in the range 30-60$\%$. With respect to
these studies, we propose a novel set of composable code
transformations targeting, for the first time, cross-loop arithmetic
intensity, with emphasis on instruction-level parallelism, redundant
computation and register locality. How such transformations generalize
to domains other than finite element local assembly will also be
discussed.
